\begin{song}{Jolene}{Dolly Parton}
		
		\chordlist{Am,C,G,Em}
		
		\textbf{Chorus:} \emph{(at the start and after every verse)}\\
		
		\begin{verse}
			Jo\chord{Am}lene, \quad Jo\chord{C}lene,\quad Jo\chord{G}lene,\quad Jo\chord{Am}lene \quad\chord{Am} \\
			I`m \chord{G}begging of you \chord{G}please don`t take my \chord{Am}man. \quad\chord{Am} \\
			Jo\chord{Am}lene, \quad Jo\chord{C}lene,\quad Jo\chord{G}lene,\quad Jo\chord{Am}lene \quad\chord{Am}\\
			\chord{G}please don`t take him \chord{Em}just because you \chord{Am}can. \quad\chord{Am}\\
		\end{verse}
		
		\begin{verse}
			Your \chord{Am}beauty is be\chord{C}yond compare, \\
			with \chord{G}flaming locks of \chord{Am}auburn hair, \\
			with i\chord{G}vory skin and \chord{Em}eyes of emerald \chord{Am}green. \\
			Your \chord{Am}smile is like a \chord{C}breath of spring, \\
			your \chord{G}voice is soft like \chord{Am}summer rain \\
			and \chord{G}I cannot com\chord{Em}pete with you, Jo\chord{Am}lene. \\
		\end{verse}
		
		\begin{verse}
			He \chord{Am}talks about you \chord{C}in his sleep, \\
			there`s \chord{G}nothing I can \chord{Am}do to keep \\
			from \chord{G}crying when he \chord{Em}calls your name, Jo\chord{Am}lene.  \\
			And \chord{Am}I can easily \chord{C}understand \\
			how \chord{G}you could easily \chord{Am}take my man, \\
			but you \chord{G}don`t know what he \chord{Em}means to me, Jo\chord{Am}lene. \\
		\end{verse}
		
		\begin{verse}
			\chord{Am}You could have your \chord{C}choice of men \\
			but \chord{G}I could never \chord{Am}love again. \\
			\chord{G}He`s the only \chord{Em}one for me, Jo\chord{Am}lene. \\
			I \chord{Am}had to have this \chord{C}talk with you, \\ 
			my \chord{G}happines de\chord{Am}pends on you, \\
			what\chord{G}ever you de\chord{Em}cide to do, Jo\chord{Am}lene.
		\end{verse}
		
	\end{song}